manuscript - APP

### 2018-10-10 R/manuscript_app.Rmd
make Figure separately, not by faceting

```{r Figure 3a}

p <- plot_fig3b()  
p

ggsave(file.path(plot_pth, "Figure3b.png"), p, width = 12, height = 6)

@@

# Appendix

```{r}
#p_k2 <- plot_fig3(2)
#p_k4 <- plot_fig3(4)
#p_k8 <- plot_fig3(8)
#p_k16 <- plot_fig3(16)
#p_k64 <- plot_fig3(64)
#p_k64_legend <- plot_fig3(64, show_legend = T)

#gridExtra::grid.arrange(p_k2,p_k4, p_k8, p_k16, p_k64, ncol = 3)
#ggsave(file.path(plot_pth, "Fig3_k2.eps"), p_k2, width = 6, height = 6)
#ggsave(file.path(plot_pth, "Fig3_k4.eps"), p_k4, width = 6, height = 6)
#ggsave(file.path(plot_pth, "Fig3_k8.eps"), p_k8, width = 6, height = 6)
#ggsave(file.path(plot_pth, "Fig3_k16.eps"), p_k16, width = 6, height = 6)
#ggsave(file.path(plot_pth, "Fig3_k64.eps"), p_k64, width = 6, height = 6)
#ggsave(file.path(plot_pth, "Fig3_k64_legend.eps"), p_k64_legend, width = 6, height = 6)
# final plot was created in inkscape
```

>>>>

```{r}
p_k2 <- plot_fig3(2)
p_k4 <- plot_fig3(4)
p_k8 <- plot_fig3(8)
p_k16 <- plot_fig3(16)
p_k64 <- plot_fig3(64)
p_k64_legend <- plot_fig3(64, show_legend = T)

gridExtra::grid.arrange(p_k2,p_k4, p_k8, p_k16, p_k64, ncol = 3)
ggsave(file.path(plot_pth, "Fig3_k2.eps"), p_k2, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig3_k4.eps"), p_k4, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig3_k8.eps"), p_k8, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig3_k16.eps"), p_k16, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig3_k64.eps"), p_k64, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig3_k64_legend.eps"), p_k64_legend, width = 6, height = 6)
# final plot was created in inkscape
```

@@
